Predicting Diabetes Based on Various Factors Using logistic Regression

### 2023-11-12 manuscript/manuscript.tex
Small typo in formating
Formation of table 1

\setion{Data}
\label{sec:data}
In order to study the proposed research question on the topic of diabetes, I searched through many databases in order to find a set that had all of the information I was looking for. After exploration, I found a data set entitled "Healthcare Diabetes Data set" on the website Kaggle. The data set was originally sourced from the National Institute of Diabetes and Digestive and Kidney Diseases. The data encompasses eight different predictors including pregnancies, glucose, blood pressure, skin thickness, insulin, BMI, diabetes pedigree function, and age.

@@

>>>>

\section{Data}
\label{sec:data}
In order to study the proposed research question on the topic of diabetes, I searched through many databases in order to find a set that had all of the information I was looking for. After exploration, I found a data set entitled "Healthcare Diabetes Data set" on the website Kaggle. The data set was originally sourced from the National Institute of Diabetes and Digestive and Kidney Diseases. The data encompasses eight different predictors including pregnancies, glucose, blood pressure, skin thickness, insulin, BMI, diabetes pedigree function, and age.

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{lrrr}
      \hline
    Variable & Mean & SD & Median \\ 
      \hline
    Id & 1384.50 & 799.20 & 1384.50 \\ 
      Pregnancies & 3.74 & 3.32 & 3.00 \\ 
      Glucose & 121.10 & 32.04 & 117.00 \\ 
      BloodPressure & 69.13 & 19.23 & 72.00 \\ 
      SkinThickness & 20.82 & 16.06 & 23.00 \\ 
      Insulin & 80.13 & 112.30 & 37.00 \\ 
      BMI & 32.14 & 8.08 & 32.20 \\ 
      DiabetesPedigreeFunction & 0.47 & 0.33 & 0.38 \\ 
      Age & 33.13 & 11.78 & 29.00 \\ 
      Outcome & 0.34 & 0.48 & 0.00 \\ 
       \hline
    \end{tabular}
    \caption{Descriptive Statistics} 
    \end{table}
